Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
clarified Reach While Stay properties

Program synthesizers are an ideal fit for synthesis of %parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesise.
\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee reach while stay properties of a closed
loop system}. The solution is based on synthesising control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.

>>>>

Program synthesizers are an ideal fit for synthesis of %parametric
controllers since the semantics of programs capture effects such as FWL
precisely.  In~\cite{DBLP:conf/cdc/RavanbakhshS15}, the authors use CEGIS
for the synthesis of switching controllers for stabilising continuous-time
plants with polynomial dynamics.  The work extends to its application on
affine systems, finding its major challenge in the hardness of solving
linear arithmetic with the state-of-the-art SMT solvers.  Since this
approach uses switching states instead of linear dynamics in the digital
controller, it entirely circumvents the FWL problem.  It is also not
suitable for the kind of control we seek to synthesise.

%\textcolor{red}{Cristina: can you please revise this sentence:
Moreover, in \cite{DBLP:conf/emsoft/RavanbakhshS16} the same authors 
use a CEGIS-based approach for synthesising continuous-time switching
controllers that guarantee Reach While Stay properties of closed
loop systems, i.e., properties that specify a set of goal states and safe states.%}. 
The solution is based on synthesising control Lyapunov
functions for switched systems, that yield switching controllers with
a guaranteed minimum dwell time in each mode.
